\documentclass[]{rahulworld-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.38\textwidth} 
\begin{large}
	\headername{Nandan M}\\
\end{large}
\section{M.Tech. | NIT Rourkela}
\vspace{0.2 cm}
Computer Science \&  Engg.\\
DOB: 06 July 1998\\
Contact: +91 7795607374\\
Email.:\textbf{\href{mailto:nandanm98@gmail.com}{nandanm98@gmail.com}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{7cm}{0.4pt}\\
\datecolor{JUNE 2023}
\subsection{M.Tech., CSE}
NIT Rourkela \\
CGPA : 8.44/10\\
\vspace{4pt}
\datecolor{August 2020}
\subsection{B.E., CSE}
Dayanada Sagar College of Engineering, Bangalore \\
CGPA : 8.69/10\\
\vspace{4pt}
\datecolor{March 2016}
\subsection{Intermediate}
Christ Academy ICSE School, Bangalore\\
Percentage: 92.2\%\\
\vspace{4pt}
\datecolor{March 2014}
\subsection{Matriculation}
Christ Academy ICSE School, Bangalore\\
Percentage: 92\%\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}  %add CodeChef, Behance etc if you wish to
\noindent\rule{7cm}{0.4pt}
\\\href{https://github.com/Technought}{\custombold{Github:// Technought}} \\
\href{https://www.linkedin.com/in/nandan-m-352035132/}{\custombold{LinkedIn://  in/nandan-m-352035132}}\\
\href{https://www.credly.com/users/nandan-m.708f12b0}{\custombold{Credly:// users/nandan-m.708f12b0}} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{7cm}{0.4pt}
\subsection{General Programming}
Java, Python, C, C++, Javascript
\vspace{6pt}
\subsection{Frameworks}
Spring Boot, Docker, Kubernetes, Selenium,\\
Jenkins, Terraform, RabbitMQ, Apache Kafka
\vspace{6pt}
\subsection{Other Tools \& Softwares}
Git, IntelliJ IDE, Eclipse,\\
Vagrant, Oracle SOA Suite
\vspace{6pt}
\subsection{Languages}
English, Kannada, Hindi, Telugu
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{7cm}{0.4pt}
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Data Structures $\&$ Algorithm\\
Operating Systems\\
Database Management\\
Computer Networks\\
Cloud Computing\\
Software Testing\\
\end{minipage}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.57\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects} %Combine projects and work experiences, and mention only relevant projects in brief
\noindent\rule{11 cm}{0.1pt}


\datecolor{}  \runsubsection{Customer Registration Fraud Detection} 
\noindent
\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{2pt}}
\runsubsection{[Docker, Kubernetes, Spring boot, Kafka, PostgreSQL, Twilio]}\\\\
Project is made using a microservices architecture containing customer and fraud services. The Customer service receives the registration request and then forwards it to the fraud service for detection.
\end{minipage}
\sectionsep

\datecolor{} \runsubsection{Remote Lab}
\noindent
\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{2pt}}
\runsubsection{[Docker, Arduino, Node.js, OpenCV, PostgreSQL]}\\\\
Present the current IOT lab coursework using an online platform to students. Exposing the currently available hardware and sensors on the online platform to run lab experiments remotely.
\end{minipage}
\sectionsep

\datecolor{}  \runsubsection{Hotel Management System}
\noindent
\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{2pt}}
\runsubsection{[Spring boot, ReactJS, PostgreSQL]}\\\\
Hotel management system with role based identity management. Dashboards with different data according to the role. Customers can register and book rooms and services provided by the hotel.
\end{minipage}
\sectionsep

\datecolor{}  \runsubsection{DinoGame Automator}
\noindent
\hspace{5em}%
\begin{minipage}{1\textwidth\vspace{2pt}}
\runsubsection{[Python]}\\\\
Automated the Dinosaur game of Google chrome using pyautogui and python imaging library Pillow.
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/Certifications} 
\noindent\rule{11cm}{0.4pt}
\datecolor{2019} \runsubsection{AWS Certified Solutions Architect – Associate}
\descript{AWS}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
 AWS Certified Solutions Architect – Associate
\end{minipage}
\datecolor{2022} \runsubsection{AZ-900: Azure Fundamentals}
\descript{Azure}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
\runsubsection{}
 Azure Fundamentals
\end{minipage}
\datecolor{2019} \runsubsection{Introduction to Internet of Things}
\descript{NPTEL}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Completed a course on IoT offered by NPTEL
\end{minipage}
\datecolor{2020} \runsubsection{Computer Security and Systems Management
}
\descript{Coursera}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Completed a course on Computer Securit offered by University of Colorado.
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Extra Curriculars
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extra Curricular Activities} %only mention activities that show job-related skill development such as creativity, positions of responsibility, presentation etc.
\noindent\rule{11cm}{0.4pt}
\datecolor{2013-2016} \runsubsection{Basketball Team}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
I have been a part of the school basketball team till 12 stardard in school.
\end{minipage}
\datecolor{2021-2023} \runsubsection{Team Head, Membership Team}
\descript{PMSF}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
I have been part of the Project Management Student Forum membership team
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}
